Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-26 prop_iop.tex
prop_iop.tex Updating here and there...

\theoremstyle{remark}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{thm}{Theorem}
\newtheorem{lemma}{Lemma}

@@

\begin{definition}[Cryptodeterministic Measure]\label{def:CryptodeterministicMeasures}Given
the set of events~$\events$, a \emph{cryptodeterministic measure}
is a function~$\pmeas:\events\rightarrow\left\{ 0,1\right\} $ such
that: 
\begin{itemize}
\item $\pmeas(\emptyset)=0$, 
\item $\pmeas(\Omega)=1$, 
\item for every event $E$, $\pmeas\left(\Omega\backslash E\right)=1-\pmeas\left(E\right)$
where $\Omega\backslash E$ is the complement event of $E$, and 
\item for every collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise
disjoint events, $\pmeas\left(\bigcup_{i=1}^{N}E_{i}\right)=\sum_{i=1}^{N}\pmeas(E_{i})$. 
\end{itemize}
\end{definition}

@@

Raised by Einstein, Podolsky, and Rosen~\cite{EPR1935,peres1995quantum},
it was a famous question whether quantum mechanics have any change
to be improved and predict unambiguously, rather than probabilistic.
One of the ``no'' answer was due to the Kochen-Specker theorem.

@@

Similarly, we can recast the result of cryptodeterminism to quantum
interval-valued probability measures as well. In another word, for
any classically event space~$\events$,there is always a classical
interval-valued probability measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $.
However, given a Hilbert space of dimension~$d\ge3$, there is no
quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $
by the Kochen-Specker theorem. The Kochen-Specker theorem provides
an example that quantum interval-valued probability measures behave
differently from the classical one, and the convexity and core in
the next section provides another example that quantum interval-valued
probability measures behave unexpectedly.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Examples for Quantum Interval-valued Probability Measures\label{sec:Examples-for-QuantumIVPM}}

>>>>

\theoremstyle{remark}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{thm}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{cor}{Corollary}

@@

\begin{definition}[Classical Cryptodeterministic Measure]\label{def:CryptodeterministicMeasures}Given
the set of events~$\events$, a \emph{classical cryptodeterministic
measure} is a function~$\pmeas:\events\rightarrow\left\{ 0,1\right\} $
such that: 
\begin{itemize}
\item $\pmeas(\emptyset)=0$, 
\item $\pmeas(\Omega)=1$, 
\item for every event $E$, $\pmeas\left(\Omega\backslash E\right)=1-\pmeas\left(E\right)$
where $\Omega\backslash E$ is the complement event of $E$, and 
\item for every collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise
disjoint events, $\pmeas\left(\bigcup_{i=1}^{N}E_{i}\right)=\sum_{i=1}^{N}\pmeas(E_{i})$. 
\end{itemize}
\end{definition}

@@

Raised by Einstein, Podolsky, and Rosen~\cite{EPR1935,peres1995quantum},
it was a famous question whether quantum mechanics have any change
to be improved and predict unambiguously, rather than probabilistic.
One way to formulate this question is to ask whether we can model
the whole quantum theory by quantum cryptodeterministic measures.

\begin{definition}[Quantum Cryptodeterministic Measure]\label{def:QuantumCryptodeterministicMeasures}Given
a Hilbert space $\Hilb$ with its set of events~$\events$, a \emph{quantum
cryptodeterministic measure} is a function~$\pmeas:\events\rightarrow\left\{ 0,1\right\} $
such that: 
\begin{itemize}
\item $\pmeas(\mathbb{0})=0$, 
\item $\pmeas(\mathbb{1})=1$, 
\item for every event $P$, $\pmeas\left(\Omega\backslash P\right)=1-\pmeas\left(P\right)$
where $\Omega\backslash P$ is the complement event of $P$, and 
\item for every collection $\left\{ P_{i}\right\} _{i=1}^{N}$ of pairwise
disjoint events, $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\pmeas(P_{i})$. 
\end{itemize}
\end{definition}

The answer is ``no'' due to the Kochen-Specker theorem.

@@

Similarly, we can recast the result of cryptodeterminism to quantum
interval-valued probability measures as well. In another word, for
any classically event space~$\events$,there is always a classical
interval-valued probability measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $.
However, given a Hilbert space of dimension~$d\ge3$, there is no
quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $
by corollary~\ref{cor:Kochen-Specker-IVPM} of the Kochen-Specker
theorem. The Kochen-Specker theorem provides an example that quantum
interval-valued probability measures behave differently from the classical
one, and the convexity and core in the next section provides another
example that quantum interval-valued probability measures behave unexpectedly.

@@

\begin{cor}\label{cor:Kochen-Specker-IVPM}Given a Hilbert space
of dimension~$d\ge3$, there is no quantum interval-valued probability
measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $.\end{cor}

\begin{proof}We are going to prove by contradiction! Suppose there
is a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\left\{ \imposs,\necess\right\} $.
Consider $\mu:\events\rightarrow\left[0,1\right]$ defined by
\begin{equation} 
\mu(P)=\cases{ 
0 & if $\bar{\mu}(P)=\imposs$ ;\\ 
1 & if $\bar{\mu}(P)=\necess$ .
}\label{cor:Kochen-Specker-IVPM} \end{equation}
 We are going to verify that $\mu$ is a cryptodeterministic measure
so that contradicts to the Kochen-Specker theorem.
\begin{itemize}
\item Since $\bar{\mu}(\mathbb{0})=\imposs$, we have $\mu(\mathbb{0})=0$.
\item Since $\bar{\mu}(\mathbb{1})=\necess$, we have $\mu(\mathbb{1})=1$.
\item For every event $P$, we have 
\begin{equation}\eqalign{ 
& \pmeas\left(P\right)=0\\ 
\Rightarrow & \bar{\mu}(P)=\imposs\\
\Rightarrow & \bar{\mu}(\Omega\backslash P)=\left[1,1\right]-\imposs=\necess\\
\Rightarrow & \pmeas\left(\Omega\backslash P\right)=1=1-\pmeas\left(P\right)\textrm{ .}
}\end{equation}
Similarly, when $\pmeas\left(P\right)=1$, we also have $\pmeas\left(\Omega\backslash P\right)=1-\pmeas\left(P\right)$.
\item Given a collection $\left\{ P_{i}\right\} _{i=1}^{N}$ of pairwise
disjoint events. 
\begin{itemize}
\item If $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=1$, then we have $\necess=\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})$
so that $\necess=\sum_{i=1}^{N}\bar{\mu}(P_{i})$, i.e., $\sum_{i=1}^{N}\pmeas(P_{i})=1=\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)$.
\item If $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=0$, then we have $\imposs=\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})$
so that $\imposs=\sum_{i=1}^{N}\bar{\mu}(P_{i})$, i.e., $\sum_{i=1}^{N}\pmeas(P_{i})=0=\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)$.
\end{itemize}
\end{itemize}
\end{proof}

\section{Examples for Quantum Interval-valued Probability Measures\label{sec:Examples-for-QuantumIVPM}}
